Eco-evolutionary dynamics of finite populations from first principles

### 2023-03-15 ind_files/02_math_background.tex
Correct minor typo

for two `nice'\footnote{We just need the solution $x(t)$ to be a continuous function} real functions $f$ and $g$, then, given any real function $h$, we can calculate how teh quantity $h(x)$ changes using the chain rule of differentiation, which says that

>>>>

for two `nice'\footnote{We just need the solution $x(t)$ to be a continuous function} real functions $f$ and $g$, then, given any real function $h$, we can calculate how the quantity $h(x)$ changes using the chain rule of differentiation, which says that
